\subsection*{What is this?}

This is a straight port of \href{http://cxx.uclibc.org/}{\tt u\-Clibc++} for \hyperlink{struct_arduino}{Arduino}. I have cut nothing out and held nothing back. Use with care!

That said, I have used u\-Clibc++'s own internal configuration to pare back un-\/needed stuff, like support for floats, gratuitous template instantiations and other things. See \hyperlink{system__configuration_8h}{system\-\_\-configuration.\-h} for all of those gory details.

Plus I added in \href{http://andybrown.me.uk/ws/2011/01/15/the-standard-template-library-stl-for-avr-with-c-streams/#IDComment246044033}{\tt Andy Brown's} excellent ohserialstream class for managing the Hardware\-Serial as an ostream.

\subsection*{How do I install it?}

This is installed just like a regular \hyperlink{struct_arduino}{Arduino} library. Unpack the contents of the distribution into the 'libraries' folder under your sketchbook. For example, my sketchbook is at /home/maniacbug/\-Source/\-Arduino, so this library is in /home/maniacbug/\-Source/\-Arduino/libraries/\-Standard\-Cplusplus .

Be sure to reset your \hyperlink{struct_arduino}{Arduino} I\-D\-E after installing it.

\subsection*{How do I try it out?}

From the \hyperlink{struct_arduino}{Arduino} I\-D\-E, navigate the menus to\-: File $>$ Examples $>$ Standard\-Cplusplus $>$ string\-\_\-vector

Upload that, set your serial monitor to 57600 baud, and check the output.

\subsection*{How do I learn more?}

The web is your friend. \href{http://cplusplus.com/reference/}{\tt cplusplus.\-com} is my personal favorite reference.

\subsection*{Which versions does it work with?}

\hyperlink{struct_arduino}{Arduino} 1.\-0 and beyond.

\subsection*{What is the license?}

u\-Clibc++ is L\-G\-P\-L, so this port is also. Andy's $<$serstream$>$ file is actually C\-C-\/\-B\-Y-\/\-S\-A, however he indicated he'd be releasing it using the 3-\/clause modified B\-S\-D license, so it will be fully compatible with u\-Clibc++. 